Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-05-12 paper.tex
Section about Feature Selection Revised and Improved

Then, a Feature Selection (FS) process  has
been carried out, as  It is an effective dimensionality reduction
technique and an essential preprocessing method to discard `noisy'
(non-useful) features \cite{Krishnapuram2004}.

The aim of these
% Did you know there were noisy features? Why?

algorithms is exploring the space of attributes to find out which
subset of them yields the best results in a classification or
prediction problem.

Moreover, the application of FS also aims to reduce the computational time for building the forecasting models, along with the complexity of the obtained models themselves. This has been a key factor in this work since one of the objectives is to obtain `easily' interpretable decision models, which can be useful for human experts (publishers).

Preprocessing a dataset means that it is revised in order to reduce errors, such as wrong or duplicated patterns, or for completing missing values. The aim is to look for the correctness,
homogeneity, and completeness of the data. % useless paragraph - JJ

%You need to lay out to the reader what you are going to do here. In
%order to reach objective x, we need to do y, that is why we use
%z. After using z, we prove that we have done y and thus reached
%objective x. For instance
% A exploratory data analysis that shows the distribution of variables
% as well as a priori clusters is the first phase in any data
% processing method
% (BTW, you should include data visualization in problem description,
% because it shows the distribution of problem variables and then
% suggests ways to deal with it) - JJ
% and so on...

After this process, the features describing every pattern are frequently analysed.
In this case, among the variables describing a new book, some may affect 
predictions as they provide information, while others may not be 
necessary and even redundant.

% You have to justify its application to this particular problem. What
% was the runnning time with all variables? What reduction was your
% target? - JJ
Additionally, the algorithm running time grows with the number of
features, making it impractical for problems with a large number of features 
\cite{Selvakuberan2008}. Feature reduction is a task that is usually
applied in these kind of situations, having two ways of performance
\cite{kittler1986feature}: feature extraction and feature selection.  
% two ways of performance? WTF? Do you mean "being performed in two
% different ways?" - JJ
%Feature selection task is usually carried out by 
%searching through all possible combinations of features, evaluating each one.

@@

Feature extraction is a ``transformation-based approach'', therefore
it transforms the original meaning of the features. This approach
involves creating a subset of new features by combinations of the
existing features, thus it is employed when the semantics of the
original dataset will not be needed by any future process. On the
contrary, feature selection attempts to retain the meaning of the
original feature set. It is part of what is called semantic-preserving
techniques, known as ``selection-based approaches". By searching
through all possible combinations of features, the aim of these
techniques is to determine a minimal feature subset to reduce
processing time, while obtaining the same or higher accuracy as the
initial feature set \cite{liu1998feature}. In the problem this work
addresses, it is very important to maintain the semantics of the set of
initial variables, and therefore several feature selection methods
have been applied.

In addition, in order to reduce the dimensionality of the input data
and to choose an appropriate set of variables, the Self-Organizing Map
(SOM) \cite{kohonen1998} method has been also applied as a `subjective' (based on expert's opinion) feature selection technique based on the visualisation of the data as a set of 2D planes (one per feature of the dataset), and their interpretation for finding out relationships between these features.

@@

With respect to feature selection methods, the used Weka software separates the process into two parts:

@@

Thus, in this research five forecasting methods, based on the literature 
review in the introduction 
\cite{Madsen2008,ChingChin2010,Thomassey2012,Xia2012,SThomassey2014}, have been used. 
Well known forecasting methods implemented in the Weka tool
\cite{Hall2009,Witten2011} have been chosen, as these methods are
widely known, and could be very helpful for practitioners to reproduce
experiments and even to solve similar sales prediction problems using
these methods. % Why these and not others? Exploratory data analysis?
               % - JJ

>>>>

At this stage, a Feature Selection (FS) process has been carried out, since it is an effective dimensionality reduction technique and an essential preprocessing method to discard less relevant or non-useful features \cite{Krishnapuram2004}.

The aim of these algorithms is exploring the space of attributes to find out which subset of them yields the best results in a classification or prediction problem. To this end, the features describing every pattern are analysed. In this case, among the variables describing a new book, some may affect predictions as they provide information, while others may not be necessary and even redundant.

The application of FS also aims to reduce the complexity of the obtained forecasting models themselves, which, in turn, implies a reduction in the computational time for building these models. The first has been a key factor in this work, because one of the objectives is to obtain `easily' interpretable decision models, which can be useful for human experts (publishers).
Regarding the algorithm running, it time grows with the number of
features, making it impractical for problems with a large number of features 
\cite{Selvakuberan2008}, but this is a secondary objective in this work.
%You need to lay out to the reader what you are going to do here. In
%order to reach objective x, we need to do y, that is why we use
%z. After using z, we prove that we have done y and thus reached
%objective x. For instance - JJ
% Antonio - Now it has been explained

% You have to justify its application to this particular problem. What
% was the runnning time with all variables? What reduction was your
% target? - JJ
% Antonio - I have explained before. The aim is not reducing the time, but the complexity of the obtained models in order to be more useful for a human

@@

FS is one of the ways of performing a feature reduction, the other one is feature extraction \cite{kittler1986feature}. 
Feature extraction is a `transformation-based approach', therefore
it transforms the original meaning of the features. This method
involves creating a subset of new features by combinations of the
existing features, thus it is employed when the semantics of the
original dataset will not be needed by any future process. On the
contrary, FS attempts to retain the meaning of the
original feature set. It is part of what is called semantic-preserving
techniques, known as `selection-based approaches' \cite{liu1998feature}. 
In the problem this work addresses, it is very important to maintain the semantics of the set of initial variables, and therefore just FS methods have been applied.

We have used some numerical FS methods included in Weka software \cite{Hall2009,Witten2011}. This tool separates the process into two parts:

In addition, in order to reduce the dimensionality of the input data
and to choose an appropriate set of variables, the Self-Organizing Map
(SOM) \cite{kohonen1998} method has been also applied as a `subjective' (based on expert's opinion) FS technique based on the visualisation of the data as a set of 2D planes (one per feature of the dataset), and their interpretation for finding out relationships between these features.

@@

@@

Thus, in this research five forecasting methods, based on the literature 
review in the introduction 
\cite{Madsen2008,ChingChin2010,Thomassey2012,Xia2012,SThomassey2014}, have been used. 
Well known forecasting methods implemented in the Weka tool have been chosen, as these methods are widely known, and could be very helpful for practitioners to reproduce experiments and even to solve similar sales prediction problems using
these methods. % Why these and not others? Exploratory data analysis?
               % - JJ
